\chapter{Background}\label{C:Background}

\par This project aims to gather data in order to ultimately form a theory on the influences of security practices in New Zealand. This chapter includes some background on what security is, the importance of information security practices, widely used security practices and summaries on existing research on the similar subject matter. 

\section{What is Security?}
\par Three objectives define security; Confidentiality, Integrity and Availability, most commonly referred to as the CIA triad \cite{craigbook}. The triad measures, controls and protects information assets which include hardware, software, firmware,  information data and telecommunications \cite{nist}. A now common synonym for security is the term coined; cybersecurity \cite{nist}. 
\newline
\par Confidentiality is the act of maintaining the protection of information from threat agents \cite{craigbook}. This term also encapsulates privacy where "individuals control or influence what information related to them may be collected and stored and by whom and to whom that information may be disclosed\cite{craigbook}. Integrity is the maintenance of data so that information and programs are only changed when needed by authorised bodies \cite{craigbook}. It also covers system integrity where "a system performs its intended function in an unimpaired manner, free from deliberate or inadvertent unauthorised manipulation of the system" \cite{craigbook}. Availability is the act of ensuring reliable access to information to authorised users \cite{craigbook}.  Any breach of these principles can result in significant adverse impacts on reputation, health and safety, service delivery, as well as finances \cite{imp}.

\section{Information Security in New Zealand}

\par A study run by Aura Security showed a 10\% increase in cyber-attacks on New Zealand businesses between the years of 2018-2019 \cite{aura}. In NZ, the rise is attributed to the digitisation of day-to-day way-of-life; as new technologies continually develop, there is an urgency to deploy products. There is a lot of pressure on programmers to finalise these products, and the deviation of attention to the finished output means that there are many new threats to security \cite{securitystrat}. Malicious attackers are also becoming more sophisticated. Individual threat attackers now seem to have the same knowledge and resources as nation-backed threat actors \cite{securitystrat}.
\newline
\newline
Areas of improvement identified by the New Zealand government are \cite{securitystrat}:

\begin{enumerate}
    \item \textbf{Cyber security-aware and active citizens:} Increased regular awareness campaigns and education opportunities for the public in regards to best personal security practices. 
    \item \textbf{Strong and capable cybersecurity workforce and ecosystem:} Increased promotion and support of the development of the cyber industry in New Zealand.
    \item \textbf{Internationally active:} Detect and prevent any breaches as well as proactively maintaining international relationships regarding information security and participating in any rule reforms. 
    \item \textbf{Resilient and responsive New Zealand:} Supporting infrastructure, businesses, charity organisations, community organisations, individuals in improving security capabilities and resilience.
    \item \textbf{Proactively tackle cybercrime:} Increasing support to impacted parties,  preventing and encouraging reporting of any cybercrimes. 
\end{enumerate}

\par These five principles are planned to continue to improve upon till 2023 \cite{securitystrat}. It is expected that aspects of these will influence the security practices that programmers use in NZ industry.

\section{Secure Programming Practices}

Without a focus on security while programming, there is a lack of confidence in the outputted security, resulting in the lack of use and waste of time, effort and money. Using unsecured programs poses significant adverse impacts to businesses and individuals.  
\newline
\par The Open Web Application Security Project (OWASP) has outlined a checklist to ensure that code is secure. They have provided this document which spans various languages and technologies as the non-profit foundation aims to improve the security across all software. It states that it is "much less expensive to build software than to correct security issues" \cite{owasp}.
\newline
\newline
Significant items from the checklist include \cite{owasp}: 

\begin{itemize}
\item \textbf{Input Validation:} This is the act of validating that all inputs are trusted. Examples of inputs are data from databases, file streams, as well as client-provided data. Anything classed as 'untrusted',  should fail and result in a rejection. The application should have one input validation routine, a specified standard character set and all validation should occur on a preset trusted system. 
\item \textbf{Output Encoding:} Data sent back the client needs to be output encoded. To make this secure, a started test routine has to be utilised, and similar to input validation; all encoding must occur on a preset trusted system. 
\item \textbf{Authentication and Password Management:} This is verifying whether a user is allowed to act. Best practice is restricting all resources except the ones intended to be public. All authentication controls should be able to fail in order to maintain security, and passwords need hashing.  In order to pass, authentication has to occur first, and every detail has to match the protected records. 
\item \textbf{Session Management:} A session should only associate the same client ID. It can only occur after authentication. 
\item \textbf{Access Control:} Set users access based on system permissions. It should use only preset, trusted systems. 
\item \textbf{Cryptographic Practices:} All assets should be protected by cryptography. A policy should be established in how to manage the public and private keys. 
\item \textbf{Error Handing and Logging:} All application errors must be 'caught' and handled. They should not disclose any information in the error responses, and instead, only show in the logs. A few can only access the logs themselves, and mechanisms should be in place to analyse the logs. 
\item \textbf{Data Protection:} Protect most assets, communications and caches. Encrypt any stored information that holds significant value. 
\item \textbf{Communication Security:} Encrypt any communication channels. Certificates should be valid, and the protocol Transport Layer Security should be in use. 
\item \textbf{System Configuration:} Ensure that everything is up to date. This includes servers, frameworks, components, languages, IDE's and libraries. Remove unnecessary information before deployment; test code, TODO's, HTTP methods and response headers. 
\item \textbf{Database Security:} Maintain short connections. Authentication needs to be checked prior use, and access control needs to be restricted. 
\item \textbf{File Management:} Require authentication and access control before any interaction with files. Validate file headers. Implement safe uploading by scanning for any malicious intent; viruses and malware. 
\item \textbf{Memory Management:} Check buffers. If larger than expected, potentially has malware or viruses. Avoid the use of vulnerable functions - \textit{printf, strcpy}
\item \textbf{General Coding Practices:}
\begin{itemize}
\item Use tested and trusted components for tasks
\item Restrict users from altering code in any way
\item Review all third party components; code and libraries
\item Initialise all variables and fields
\end{itemize}
\end{itemize}

\newpage
\section{Related Work}

A small literature review was undertaken to gain insights on similar studies.

\subsection{Think secure from the beginning}

In “A Survey with Software Developers” \cite{summary1}, the authors investigate the human behaviours and motivations surrounding factors of software security. The authors specified a series of questions targeted toward software developers through an online survey. The research examined responses to support the professional development of programmers further, both in theory and practice. This was chosen as background reading as it aligns well with the research goals of “Why Do Programmers Do What They Do?”, as it aims to form a theory on the influences and effects of decisions surrounding technical work. 
\newline
\newline
The results outlined the following common groups:

\begin{enumerate}
\item \textbf{Work Motivation:} Developers did not lack motivation in their job. They performed based on self-determination.
\item \textbf{Understanding of software security:} Developers had a sound understanding of software security. They grasped the importance of securing technical work and the discussed various methods of doing so and specifying at what stages in the project life-cycle they should implement these based on “best practices”.
\item \textbf{Security Issues:} Majority of the participants believed their software could be compromised, despite being comfortable with the approaches to protecting the software. The majority has also experienced a security issue, whether that be a breach or vulnerable code.
\end{enumerate}

\par From these common groups, the overarching theme displayed was that the developers were not purposefully ignorant about maintaining security practices; the majority were proactive and willing to learn. However, it was the importance of functionality and lack of ongoing support from organisations which made working towards a more secure software challenging. 
\newline
\par This paper was valuable to read as there are strong similarities between the research topic developed in this and the subject of this ENGR489 project. The methodologies are different; however, this paper's findings display a programmers personal perspective rather than a theorised view. It is a direct comparison to our project, and we can further outline questions directed to the future work stated in the article’s conclusion; “to explore potential relationships between motivations, deterrents and strategies for software security” and “investigate security procedures and attitudes in companies that have experienced security breaches and compare it to others who have not”. 
\newline
\par Similar questions from the survey were used for the interview process in this study. Important questions identified are:

\begin{itemize}
\item How does security fit in the development life-cycle in real life? 
\item What are the current motivators and deterrents to developers paying attention to security? 
\end{itemize}

The differences and similarities can be easier understood in the table below:
\newline
\begin{table}[htb]
\begin{tabular}{|l|l|l|}
\hline
\multicolumn{1}{|c|}{} &
\multicolumn{1}{|c|}{\textbf{This Research}}              & \multicolumn{1}{c|}{\textbf{Assal and Chiasson's Research}} \\ \hline
\textbf{Data Collection} & Interview                 & Survey                 \\ \hline
\textbf{Participant Group}                  & Any type of programmer  & Software Developers                                        \\ \hline
\textbf{Location}             & New Zealand        & North America   \\ \hline
\textbf{Data Type}     & Confidential & Anonymous \\ \hline
\textbf{Results}              & Analysis of participant answers and observations & Based on participant answers                  \\ \hline
\textbf{Topic}                & Security                  & Security \\ \hline
\end{tabular}
\centering
\newline
\caption{Summary of comparison with "Think secure from the beginning"}
\centering
\end{table}

\subsection{Software Development Practices in New Zealand}

\par In “Software Development Practices in New Zealand” \cite{summary2}, the report authors look to “developing and applying a range of software productivity techniques and tools to enhance the performance of the New Zealand software industry”. Like Assal and Chiasson, the authors of this study outlined a series of questions in a survey targeted towards known Information Technology organisations. The survey aimed to understand the practices used by industry and in the findings can be used to make recommendations on best-use development practices for organisations. Kirk and Tempero’s report is similar in output to the ENGR489 project as the findings can be used to make suggestions for teams adopting and developing security practices. This was chosen as a background reading as it provides insights on the current state of industry in New Zealand, which is what I aimed to develop in the research outlined in this report. 
\newline
\newline
The key findings of this study were:

\begin{enumerate}
\item Organisations and individuals \textbf{do not follow} standard agile process models.
\item New Zealand is generally more \textbf{implementation-focused} in software development. There is an emphasis on this over other aspects of the software development life-cycle such as security and testing. 
\item Decision-making is a \textbf{collaborative effort} with individuals involved in different stages and traits of the development life-cycle. 
\item While most New Zealander's state they are "agile" this is not supported as frequent contact with clients and stakeholders is not upheld. However, there is a \textbf{highly iterative aspect} to the work individuals do on projects which do maintain agile principles. 
\item There is a \textbf{weakness in requirements gathering} which results in a widely noticed lack of clarity on scope details. 
\item This point also relates to point 2, there is a noticed severe \textbf{lack of code quality} whether this is in design, reviewing and testing stages, or with general coding best practices. 
\item Most \textbf{do not develop around }tools such as libraries - rather they use them as a support. This can be derived as not being "best-practice" and can be more time-consuming. 
\end{enumerate}

\par Not much was asked specific to security, but finding number 6 links to poor practices around secure programming. 
\newline
\par The report had a limitation in which it did not make any recommendations at this stage, but it did mention that these findings can be used by organisations to obtain a view of the software practices in New Zealand. From here, organisations can make their own decisions on what to focus on to better their specific operations.  
\newline
\par Comparing to the described ENGR489 project, the methodology is different, and while the topics to are differing, they are similar enough to make interesting comparisons between the two. Kirk and Tempero focus on software development practices, while this project will research security practices. A comparison that can be made could be between the findings, as much like the prior related work; the findings are that of a personal perspective of the participants rather than an objective view which Grounded Theory supplies.
\newline
\par The differences and similarities are outlined in the table below:
\newline
\newline
\begin{table}[htb]
\begin{tabular}{|l|l|l|}
\hline
\multicolumn{1}{|c|}{} &
\multicolumn{1}{|c|}{\textbf{This Research}}             & \multicolumn{1}{c|}{\textbf{Kirk and Tempero's Research}} \\ \hline
\textbf{Data Collection} & Interview                 & Survey                  \\ \hline
\textbf{Participant Group}                  & Any type of programmer  & If developing software           \\ \hline
\textbf{Location}             & New Zealand         & New Zealand      \\ \hline
\textbf{Data Type}     & Confidential & Anonymous  \\ \hline
\textbf{Results}              & Analysis of participant answers and observations & Based on participant answers                 \\ \hline
\textbf{Topic}                & Security                  & Software Best Practices \\ \hline
\end{tabular}
\centering
\newline
\caption{Summary of comparison with "Software Development Practices in New Zealand"}
\centering
\end{table}







