\chapter{Work Completed}\label{C:Completed}

\par As of yet, the progress made has focused on the human ethics application as well as crafting appropriate interview questions. Before any contact with potential interview participants, the human ethics application has to be approved. This is to ensure that research follows responsible and robust processes involving people and their data, consequently, proceeding ethically. As this has been in a recursive stage of editing and sending back to be reviewed, there has been parallel iterative work designing potential questions for the semi-structured interview—processes which have involved pilot studies in order to focus on an area of the topic. As the human ethics application is yet to be approved, the data collection and analysis stages have not started. Each of the areas is discussed in detail in the following sections. 

\section{Human Ethics Application}

\par There was an immediate pressure to complete the human ethics application as the rest of the project is highly dependent on the participant interviews. This meant that the research had to be planned quite quickly in order to provide the human ethics committee with all the relevant information needed to approve the application. The initial application was submitted 8th of April. It has since undergone pre-committee revisions and post-committee revisions and is currently pending a second committee review. This application outlined a series of multichoice and short-answer questions which had to be answered thoroughly and supporting documents had to be submitted. These supporting documents included the participant information sheet, consent to interview document, an interview guide, and as this research’s recruitment will be done through mailing lists and Meetup and LinkedIn posts, a sample recruitment post has also been supplied. 
\newline
\par The human ethics application specified essential methods for ethical data collection in order to maintain research that followed the ideal human ethics policy \cite{hepol}. The application went into details of data collection and recruitment, conformation with the university Te Tiriti o Waitangi statute, project risks, and data management. Answering these sections meant that much planning has gone into the interview process for data collection. In particular, it has been decided that the selection process will follow purposeful sampling for the interviews. This is because the selection of participants will need to occur based on whether they are professional programmers in the industry. The study will ideally include participants with a range of job titles and years in the field in order to find interesting comparisons during the interview process in the way security practices are adopted in the developed software. Participants will consequently be filtered by appropriate job titles, and be older than the age of 18 to avoid complexities with the Vulnerable Children Act 2014 \cite{childact}.
\newline
\par Focus on the Te Tiriti o Waitangi was necessary as this is a research project run in New Zealand with participants who work in the domestic industry. Therefore, the recruitment of participants and the conducting of the interviews will run in a way which respects the principles outline in the university statute, which derive directly from Te Tiriti o Waitangi. Specific care was taken to this as there is only a certain threshold that this study can pertain to. However, it was decided that recruitment should work under the principle of Whai wāhi (participation) and encourage the participation of tangata whenua by advertising it on accessible platforms and to organisations with more of an emphasis of Te Tiriti in their core values. An alum of Maori descent was consulted on this, and they mentioned that in the participant information and consent forms, it should be explicitly clear that participants still have ownership of their data and can edit and remove information up to one week after the interview if they wish.
\newline
\par Corresponding to the point above, the interviews will be confidential rather than anonymous to allow for participant edits and to also allow for follow up questions if necessary. They will in no way be able to be identified and in any report outputs of this study will not name participants and instead, be either referred to by role or by pseudonyms. Data will also be aggregated to maintain confidentiality. Participants will also be reminded before the interview as well as in the information and consent documents, that they should not divulge any sensitive information. 
\newline
\par Due to complications with COVID-19, the interviews will also have to adapt to allow for online capabilities using applications such as Zoom. There were issues surrounding obtaining consent, and the application had to be amended to allow for electronic consent. This will be done by emailing the form to participants, and consent will be obtained by a simple email back of the agreement. The electronic signing of the form was not applicable as not everyone may have access to software with the capabilities to do so. It was also decided that the interview will offer a \$10 gift reward for participation for their time during the pandemic, and this will be a supermarket voucher. Safety was consequently paramount in the planning of the pandemic for both the interviewer and the interviewee. In the case of any in-person interviews, sanitiser and a box of tissues will be in hand as well as disinfection of the meeting rooms before and after interviews, and they will occur by maintaining social distancing practices. To thank participants for their time, they will be offered a gift voucher to a supermarket.

\section{Interview Planning}

\par In the human ethics application, planning had to occur well ahead of interviews, and there was a focus on creating the questions. However, as grounded theory involves a semi-structured interview process, a guide was submitted alongside the application. This is because questions can change dependent on the participant as well as the narrowing focus on the ultimate theory. The interviews will also include open-ended questions which allow for more personal, in-depth responses which can hold more information to be analysed. It is expected that the analysis will occur immediately after interviews in order to revise questions before the next participant.  All interviews are expected to take a maximum of 60 minutes and will be coded. The interview recordings will be available for participants at their request for any amending of content.
\newline
\par Interviews will start by collecting information on participant background. This means groupings can happen by education, roles and experience. The next section of the interview will cover the current security practices that they implement in their code. This will then lead to the impacts of security in the projects they have worked on, and any background in the testing of those practices and successes of some over others. These sections allow for the simplest of aggregations to occur when all data has been collected and analysed. 
\newline
\par For a better understanding of the process, old alums; Nathan Newton and Brendan Julian, who conducted grounded theory methodology studies were contacted on their approaches. Brendan stated that they did not know what their focus would be going into the interviews, and the idea slowly formed the more interviews and analysis he did. Nathan stated that he was almost “over-prepared” in the sense that he had read many academic articles that none of the industry members knew specifics about. Both had the similarities in which going into the interview stage; they had very broad questions that did not quite relate to each other. Those questions did not encourage the high-ended answers this study promotes. 
\newline
\par Potential interview questions have been planned alongside these sections. However, much like the issues with the alums, they are too broad and are disjointed of each other; often focusing on several different aspects of security practices. More thought is going into these questions to having a specific focus, which will provide the semi-structured interview with the flow it needs to collect concise data.
\newline
\par Some time slots have been scheduled for interviews to take place in.


\section{Pilot Study}

\par After obtaining relevant feedback on the questions, a suggestion was made to run a small pilot study.  The objective of a pilot study is to enhance the likelihood of success in the main study and to avoid any risks to completion \cite{pilot}. The first pilot study conducted was to provide evidence on the level of efficiency of the outlined potential interview questions. The efficiency being that of the potential to obtain open answers with an ultimate focus in mind. This focus will allow for more detailed answers which can be analysed to draw closer comparisons to form a more robust theory. The participant of the pilot study was another alum of the university and personal contact. This pilot solidified that the potential questions are too broad in scope. It was also highlighted that a few questions were quite similar and can be condensed. The questions were also not as opened-ended as desired, which made the answers seem not very valuable. As this pilot study was about testing the questions, the participant of the pilot study answered every potential question. This meant that this interview did not follow a typical grounded theory approach in which questions are asked dependent on the participant. 
\newline
\par For the following pilot interview, this was not an issue as with more clarity on questions. Therefore the typical grounded theory approach to interviews was followed, and questions were dependent on the interviewee. The person being another personal contact. More pointed questions were asked, but from this second interview, it is apparent that the questions need to be asked in a way that promotes discussion. As an interviewer, there also needs to be more practice in continuing the conversation and adapting questions to the last answer. 
\newline
\par Overall, this small pilot study was essential in providing some more clarity on the interview process. It also supplied practice in conducting interviews and has helped in the continuous process of defining questions. 

\section{Advertising}

\par Advertisement of this study will occur through mailing lists and websites like OWASP Meetup and LinkedIn. A recruitment post has been made for this as well as the support of a simple web-page (https://homepages.ecs.vuw.ac.nz/~sajwanlava/) \cite{webpage}. The webpage presents this study as professional and legitimate – traits especially important to programmers interested in security practices. Advertising as not started yet as the human ethics application is still pending approval. However, as everything is ready, as soon as the approval is granted, recruitment can begin. 
\newline
\par Following the principle of Whai wāhi, the recruitment post and web-page include the use of Te Reo. This is simple way of respecting tangata whenua, and is also more welcoming. 







